Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of SVMs with default parameters (C=1) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since the MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.

>>>>

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of support vector machines (SVMs) with default parameters ($C=1$) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.
